### 2016-01-19 paper.tex
Reword Re dependence of C_P curves
Remove 'we see that' per @nearyvs suggestion

Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
not collapse exactly onto each other. Note that the data collection was limited
at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
the tow carriage drive belt. However, in contrast to the power coefficient data,
the rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge
0.6 \times 10^6$.

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. We see that the power coefficient of the turbine
increases dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda
U_\infty c / \nu \approx 2 \times 10^5$, beyond which there appears to be a
small, linear, positive trend. The tendency of $C_P$ to continue increasing
slightly could be an effect of lower ``virtual camber''---or flow curvature
\cite{Migliore1980}---when compared to the strong $Re$-independence of the
higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

>>>>

The power coefficient curves do not collapse exactly onto each other, indicating
Reynolds number dependence, though the differences become relatively small as
$Re$ is increased. Note that the data collection was limited at higher $Re$ and
$\lambda$ due to the unsteady turbine force resonating with the tow carriage
drive belt. However, in contrast to the power coefficient data, the rotor drag
coefficient curves nearly collapse onto each other for $Re_D \ge 0.6 \times
10^6$.

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of lower ``virtual camber''---or flow curvature
\cite{Migliore1980}---when compared to the strong $Re$-independence of the
higher $c/R$ UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
